Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
We thank the reviewer fot this insightful comment. Indeed, it summarizes what was intended to be studied in this manuscript. Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript. Regarding Figure 2, we fixed it as recommended by the reviewer. Moreover, we applied the same procedure to voltage $V$, in order to keep consistency throughout our manuscript.

@@

\begin{resposta} 
We appreciate these comments; we actually realized that the contributions of our manuscript were unclear. We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modelling, which was already investigated in prior studies over the last two decades. Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation). Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment. This information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.

The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result), we understand that this comparison is not appropriate.

@@

The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result, as described in Section 4 of our manuscript), so we understand that this comparison is not appropriate.

@@

(7)       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? waveforms such as: Input power, VMPP, IMPP, AC load

>>>>

\begin{resposta} 
We thank the reviewer for this insightful comment. Indeed, it summarizes what was intended to be studied in this manuscript. Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modeling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript. Regarding Figure 2, we fixed it as recommended by the reviewer. Moreover, we applied the same procedure to voltage $V$, in order to keep consistency throughout our manuscript.

@@

\begin{resposta} 
We appreciate these comments; we actually realized that the contributions of our manuscript were unclear. We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modeling, which was already investigated in prior studies over the last two decades. Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation). Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment. This information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.

The authors hold real load curve and information collected from monitoring system using Raspberry Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result), we understand that this comparison is not appropriate.

@@

The authors hold real load curve and information collected from monitoring system using Raspberry Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result, as described in Section 4 of our manuscript), so we understand that this comparison is not appropriate.

@@

(7)       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? wave-forms such as: Input power, VMPP, IMPP, AC load
